Diffantom: a whole-brain diffusion MRI phantom derived from a real dataset of the \acrlong{hcp}

### 2015-08-14 paper/abbreviations.tex
new suggestions from MJL

% -*- root: main.tex -*-
% @Author: Oscar Esteban
% @Date:   2015-06-16 15:45:32
% @Last Modified by:   Oscar Esteban
% @Last Modified time: 2015-07-14 12:49:57

\newacronym{dmri}{dMRI}{diffusion MRI}
\newacronym{fa}{FA}{fractional anisotropy}
\newacronym{adc}{ADC}{anisotropic diffusion coefficient}
% \newacronym{hcp}{HCP}{Human Connectome Project}
\newacronym{fod}{FOD}{fiber orientation distribution}
\newacronym{wm}{WM}{white matter}
\newacronym{gm}{GM}{gray matter}
\newacronym{cgm}{cGM}{cortical gray matter}
\newacronym{dgm}{dGM}{deep gray matter}
\newacronym{csf}{CSF}{cerebrospinal fluid}
\newacronym{snr}{SNR}{signal-to-noise ratio}
\newacronym{csd}{CSD}{constrained spherical deconvolution}
\newacronym{cc0}{CC0}{Creative Commons Zero licence}
\newacronym{roc}{ROC}{receiver operating characteristic}
\newacronym{pve}{PVE}{partial volume effect}
\newacronym{cst}{CST}{corticospinal tract}

\newglossaryentry{hcp}
{
	name={Human Connectome Project},
	text={HCP},
	first={Human Connectome Project (HCP, \cite{essen_human_2012})},
	long={Human Connectome Project (HCP)},
	description={Human Connectome Project}
}

>>>>

% -*- root: main.tex -*-
% @Author: Oscar Esteban
% @Date:   2015-06-16 15:45:32
% @Last Modified by:   Oscar Esteban
% @Last Modified time: 2015-08-14 09:16:55

\newacronym{dmri}{dMRI}{diffusion MRI}
\newacronym{fa}{FA}{fractional anisotropy}
\newacronym{adc}{ADC}{anisotropic diffusion coefficient}
% \newacronym{hcp}{HCP}{Human Connectome Project}
\newacronym{fod}{FOD}{fiber orientation distribution}
\newacronym{wm}{WM}{white matter}
\newacronym{gm}{GM}{gray matter}
\newacronym{cgm}{cGM}{cortical gray matter}
\newacronym{dgm}{dGM}{deep gray matter}
\newacronym{csf}{CSF}{cerebrospinal fluid}
\newacronym{snr}{SNR}{signal-to-noise ratio}
\newacronym{csd}{CSD}{constrained spherical deconvolution}
\newacronym{cc0}{CC0}{Creative Commons Zero licence}
\newacronym{roc}{ROC}{receiver operating characteristic}
\newacronym{pve}{PVE}{partial volume effect}
\newacronym{cst}{CST}{corticospinal tract}
\newacronym{t1}{T1w}{T1-weighted}

\newglossaryentry{hcp}
{
	name={Human Connectome Project},
	text={HCP},
	first={Human Connectome Project (HCP, \cite{essen_human_2012})},
	long={Human Connectome Project},
	description={Human Connectome Project}
}
